---
title: "Choropleth"
author: "Barry Bullas"
date: "27 May 2019"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE, echo=FALSE, warning =FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Check if the required packages are installed, if not install them
list.of.packages <- c("leaflet", "leaflet.extras", "DT")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

#Load required packages
library(leaflet)
library(leaflet.extras)
library(DT)
```

# Chropleth maps

A choropleth map is a thematic map in which areas are shaded or patterned in proportion to the measurement of the statistical variable being displayed on the map, such as population density or per-capita income.  In this exercise we are going to produce the map below.


```{r }
#Insert example of the finished choropleth map we will build
```

## Overview of this exercise

1. Load polygon shape files
2. Load a dataset
3. Aggregate the dataset
4. Join the aggregated dataset to the polgyons
5. Visualise
6. Finishing touches

##Load polygon shape files

Explanation of polygon shape files and where to to get them from.


```{r}
#Code to load the relevant shape files
```

## Load a dataset

Explanation of the dataset used in the example

```{r }

#DataTable view to allow the user to explore the dataset
```


## Aggregate the dataset

Aggregating the data to a shapefile level, for example agregating by postcode

```{r}
#Code to aggregate the data
```

## Join the aggregated dataset to the polgyons

Join the aggregated data to the polygon

```{r}
#Code to join the data to the polygon
```

## Visualise

Now we are ready to visualise the data by colouring each polygon.  Info on colourbrewer

```{r}
#Code to colour the polygons based on the value
```

## Finishing touches

Adding legends, 

```{r}
#Adding legends to the map and other finishing touches
```








